Empirical Bayes analysis of \RNAseq{} data for detection of gene expression heterosis

### 2015-08-18 ebayes_rnaseq_heterosis.tex
include gene-specific parameter comparison

>>>>

Figure \ref{f:gene_specific_estimates} provides point estimates from the initial \edgeR{} estimation step and after the eBayes procedure described in Section \ref{s:ebayes}. 
\begin{figure}
\centerline{\includegraphics[width=\textwidth]{gene_specific_estimates.pdf}}
\caption{Two-dimensional histogram of point estimates from \edgeR{} and eBayes (posterior means) along with the $y=x$ diagonal.}
\label{f:gene_specific_estimates}
\end{figure}
This figure shows shrinkage for large absolute values of $\alpha$ and $\delta$ from the \edgeR{} estimation toward $\hat{\eta}_\alpha$ and $\hat{\eta}_\delta$ which are both approximately zero. The figure also shows decreased values for the overdispersion parameter with larger decreases for high and low values of overdispersion. Finally, very little, if any, shrinkage is observed for $\phi$.
